
\appendix

  \chapter{Licence}
  \label{appendix:a}

  The program, paper and etc. in this thesis are open source, they can be found in:
    \begin{itemize}
        \item Thesis homepage: \url{https://changkun.us/bechelorthesis/};
        \item GitHub repostory: \url{https://github.com/changkun/BachelorThesis/}.
    \end{itemize}


  %此毕业设计的程序、论文等全部源文件均已开放源代码，可以在论文主页：\url{https://changkun.us/bechelorthesis/}或 GitHub 仓库中查看：\url{https://github.com/changkun/BachelorThesis/}

  In case, all related text, picture and video content are licensed under a Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License\footnote{\url{http://creativecommons.org/licenses/by-nc-sa/4.0/}}.

  The other part in this thesis (program source code) is licensed under a GNU Public Licence Version 3.0.
  %注意，本毕业设计(论文)中的所有文字、图片及视频内容均采用知识共享署名-非商业性使用-相同方式共享(BY-NC-SA) 4.0 国际许可协议\footnote{\url{http://creativecommons.org/licenses/by-nc-sa/4.0/}}进行许可。

  %其余部分（代码）则采用 GNU Public Licence v3\footnote{\url{http://www.gnu.org/licenses/gpl-3.0.en.html}} 进行许可。

  \cleardoublepage

  \chapter{Questionnaire - Part A}
  \label{appendix:b}

  Welcome! :)
  %您好！

  Thank you for join our study! This quesionnaire is the first part of out research, we need you to fill this simple quesionnaire.
  \textbf{Quesions marked by * is required}
  %感谢您参与我们的研究！这份问卷是我们本次研究的第一部分，我们需要您填写这份简单的问卷。
  %\textbf{其中用*标注的问题是必须填写的}。

  \begin{enumerate}
      \kaishu
      %\item \textbf{请选择下面你觉得操作最舒适的多个操作*}\\
      \item \textbf{Please select the most confortable options *}
      %请选择至少五个选项
      At least five options
      \begin{itemize}
        %   \item 大拇指在食指上滑动
        %   \item 大拇指在中指上滑动
        %   \item 大拇指在无名指上滑动
        %   \item 大拇指在小指上滑动
        %   \item 大拇指和食指的快速捏合
        %   \item 大拇指和食指的长时间捏合
        %   \item 大拇指和中指的快速捏合
        %   \item 大拇指和中指的长时间捏合
        %   \item 大拇指和无名指的快速捏合
        %   \item 大拇指和无名指的长时间捏合
        %   \item 大拇指和小指的快速捏合
        %   \item 大拇指和小指的长时间捏合
        %   \item 五个手指从伸展到握拳状态
        \item Thumb swipe on index finger
        \item Thumb swipe on middle finger
        \item Thumb swipe on ring finger
        \item Thumb swipe on little finger
        \item Thumb pinch with index finger
        \item Thumb force pinch with index finger
        \item Thumb pinch with middle finger
        \item Thumb force pinch with middle finger
        \item Thumb pinch with ring finger
        \item Thumb force pinch with ring finger
        \item Thumb pinch with little finger
        \item Thumb force pinch with little finger
        \item Five fingers grab
      \end{itemize}
      \item \textbf{What would you think about strangers raising hand make some gesture which are showed on question 1?}\\
      Please write your idea
      %当你在马路、公交车、地铁等公共场所看到陌生人抬起手进行问题 1 的操作时，你会怎么想？
      %请在下方写下你的想法

      \item \textbf{Please connect the left side and right side operate options if you think they are suitable *}\\
      Options on the left side can only connect to only one option on the right side, you can pass a connection if they are not suitable.
      %\item \textbf{请连接下方左右侧的你认为的所有符合你操作直觉的两个选项*}\\
      %左侧的每个选项只能连接一个右侧选项,若没有则可不进行连接

      \begin{tabular}{ l r }
       ~ & Thumb swipe on index finger \\[-3pt]
       ~ & Thumb swipe on middle finger \\[-3pt]
       ~ & Thumb swipe on ring finger \\[-3pt]
       ~ & Thumb swipe on little finger \\[-3pt]
      Tap gesture & Thumb pinch with index finger \\[-3pt]
      Finger force touch a screen & Thumb force pinch with index finger \\[-3pt]
      Tune knob & Thumb pinch with middle finger \\[-3pt]
      Finger swipe left on a plane & Thumb force pinch with middle finger \\[-3pt]
      Finger swipe right on a plane & Thumb pinch with ring finger \\[-3pt]
       ~ & Thumb force pinch with ring finger \\[-3pt]
       ~ & Thumb pinch with little finger \\[-3pt]
       ~ & Thumb force pinch with little finger \\[-3pt]
       ~ & Five fingers grab \\[-3pt]
      \end{tabular}
  \end{enumerate}

  % \centerline{

  % }

  \cleardoublepage


  \chapter{Questionnaire - Part B}
  \label{appendix:c}

  Hi!

  Thanks for join our study, again! This questionnaire is the last part of this study, we still need you to fill the following simple questions.
  \textbf{Quesions marked by * is required}
  %感谢您参与我们的研究！这份问卷是我们本次研究的最后一个部分，我们需要您填写这份简单的问卷。
  %\textbf{其中用*标注的问题是必须填写的}。

  \begin{enumerate}
      \kaishu
      \item \textbf{Your ID*}\\
      Please write what your input here:
      \item \textbf{Age?}\\
      Please write what your input here:
      \item \textbf{Gender?*}\\
      Please choose only one of the following:
      \begin{itemize}
          \item Male
          \item Female
      \end{itemize}
      \item \textbf{Frequency of wearing watches?*}\\
      Please use "Never", "Rarely", "Sometimes", "Often", "Always" to answer these questions:
      %请对下方的问题以：从不、极少、有时、经常、总是，这五个选项来回答。
      \begin{itemize}
          \item Frequency of wear it on left hand?
          %将手表佩戴在左手的频率？
          \item Frequency of wear it on right hand?
          %将手表佩戴在右手的频率？
          \item Frequency without wear a watch?
          %不佩戴手表的频率？
          \item Frequency of forget wear it?
          %忘记带手表的频率？
      \end{itemize}
      \item \textbf{Do you have use experiences of smart watches?*}\\
      Please choose only one of the following:
      \begin{itemize}
          \item Yes
          \item No
      \end{itemize}
      \item \textbf{Which Model?*}\\
      If you choose Yes in question 5, please write this question's answer:
      %如果5中勾选了『是』，请在下方的空白处填写
      \item \textbf{How many watches you own?*}\\
      Including traditional watch and smart watch, count them even they have more than one band, write your answer here:
      %包括智能手表和传统手表,不同的表带按不同款计算, 即使不经常使用手表，请在下方的空白处填写数字
      \item \textbf{Do you still using watch in your daily life?*}\\
      Please choose only one of the following:
      \begin{itemize}
          \item Yes
          \item No
      \end{itemize}
      \item \textbf{For what reason?*}\\
      Please write what your input here:
      \item \textbf{Do you considering to buy a smart watch?*}\\
      Please choose only one of the following:
      \begin{itemize}
          \item Yes
          \item No
      \end{itemize}
      \item \textbf{For what reason?*}\\
      Please write what your input here:
      \item \textbf{What is the most significant option of using smart watch for you?*}\\
      Please choose only one of the following:
      \begin{itemize}
          \item Price
          %价格
          \item Battery
          %电池续航
          \item Habit
          %使用习惯
          \item Others, please write it down
          %其他，请写下你的原因
      \end{itemize}
      \item \textbf{If you have any comments for this study, we glad to here your voice. Please write your comments here}
      %对本次实验你是否还有其他疑问、看法，欢迎您提一些意见。}\\
  \end{enumerate}
